Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-06-23 Cover_letter_JPM.tex
4 gene signature

%***  a gene signature with deep learning CNN,
%or http://gepia2.cancer-pku.cn/#index
%https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03544-z
%https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-021-04040-8
%or
% PCA of gene signature => L1/L2 penalized Cox model; L1-penalized (Lasso) Cox proportional hazard regression model (R package glmnet)
%x Statistical methods: Development of a 13-gene signature prediction model for survival in HPV-negative OSCC patients.
%To build a prediction model for OSCC-specific survival unique to the patients with HPV-negative OSCCs\cite{Lohavanichbutr2013}.

@@

The risk score for each HNSCC sample was calculated based on the IRGP prognostic signature using the following formula:\\[0.5cm]
risk score = $expression_{gene1} \times \beta_{gene1} + expression_{gene2} \times \beta_{gene2} + ... + expression_{geneX} \times \beta_{geneX}$\\

@@

, in which $X$ was the number of IRGPs and $\beta$ was coefficient value for each IRGPs. Taking the median value of risk score as the threshold, we divided all the HCC samples into high-risk or low-risk groups. The accuracy and sensitivity of survival prediction based on the risk score were verified by receiver operating characteristic (ROC) curve analysis and determined by the value of area under the curve (AUC) in 1, 3, and 5 years. Kaplan–Meier (KM) survival curves analysis () was used to analyze the over survival (OS) of the high-risk and low-risk groups. We then integrated IRGPs with existing clinical and pathologic features for multivariate Cox regression analysis. Tumor TNM, stage, grade, age, and body mass index (BMI) were regarded as continuous variables. The association between IRGPs risk score, clinical, and pathologic features was determined by KM analysis. Prognostic risk models of tumor TNM, grade, age, and stage were constructed. Subsequently, a Cox proportional hazards regression model was constructed by combined the Tumor TNM, grade, age, stage, and risk scored. The R package rms was used to compare these models with the IRGP prognostic signature. Concordance index (C-index) was used to assess the accuracy of the prognostic biomarkers. Also, the comparison between IRGPs and clinical/pathologic features was performed by forest and nomogram plots to determine the effectiveness of the prognostic value. The statistical difference of IRGPs in the clinical/pathologic features was compared using the Kruskal–Wallis test.

@@

\end{MyColorPar}
%

>>>>

%***  a gene signature with deep learning CNN,
%or http://gepia2.cancer-pku.cn/#index

%cv.mod$glmnetRes$lambda.1se
the most regularized model with cross-validation error within 1 standard deviation of the minimum.

Finally, we use gene signature, HK1, EZR, RRAGA, and DUSP16 to predict their survival impact on TCGA HNSCC cohort (please see Figure \ref{fig:signature4}).

However, # 4 gene signature: #### 
# "EZR" has \textit{P} value $>0.05$

\begin{figure}
%    \centering
  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[width=8cm]{rplot_KMplot_HK1.pdf}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[width=8cm]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_signature4_FDRKM.pdf}  
  \end{subfigure}
    \caption{OS in TCGA for a gene signature including HK1, EZR, RRAGA, and DUSP16. Those genes have not significant survival impact if calculated individually.}
    \label{fig:signature4}
\end{figure}

%https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03544-z
%https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-021-04040-8
%or
% PCA of gene signature => L1/L2 penalized Cox model; L1-penalized (Lasso) Cox proportional hazard regression model (R package glmnet)
%x Statistical methods: Development of a 13-gene signature prediction model for survival in HPV-negative OSCC patients.
%To build a prediction model for OSCC-specific survival unique to the patients with HPV-negative OSCCs\cite{Lohavanichbutr2013}.

@@

%The risk score for each HNSCC sample was calculated based on the IRGP prognostic signature using the following formula:\\[0.5cm]
%risk score = $expression_{gene1} \times \beta_{gene1} + expression_{gene2} \times \beta_{gene2} + ... + expression_{geneX} \times \beta_{geneX}$\\

@@

%, in which $X$ was the number of IRGPs and $\beta$ was coefficient value for each IRGPs. Taking the median value of risk score as the threshold, we divided all the HCC samples into high-risk or low-risk groups. The accuracy and sensitivity of survival prediction based on the risk score were verified by receiver operating characteristic (ROC) curve analysis and determined by the value of area under the curve (AUC) in 1, 3, and 5 years. Kaplan–Meier (KM) survival curves analysis () was used to analyze the over survival (OS) of the high-risk and low-risk groups. We then integrated IRGPs with existing clinical and pathologic features for multivariate Cox regression analysis. Tumor TNM, stage, grade, age, and body mass index (BMI) were regarded as continuous variables. The association between IRGPs risk score, clinical, and pathologic features was determined by KM analysis. Prognostic risk models of tumor TNM, grade, age, and stage were constructed. Subsequently, a Cox proportional hazards regression model was constructed by combined the Tumor TNM, grade, age, stage, and risk scored. The R package rms was used to compare these models with the IRGP prognostic signature. Concordance index (C-index) was used to assess the accuracy of the prognostic biomarkers. Also, the comparison between IRGPs and clinical/pathologic features was performed by forest and nomogram plots to determine the effectiveness of the prognostic value. The statistical difference of IRGPs in the clinical/pathologic features was compared using the Kruskal–Wallis test.

@@

\end{MyColorPar}
%
\clearpage
